---
title: "Region Sales of Top 100 Video Games"
author: "Siyi Wang"
date: 2021-11-11T21:13:14-05:00
categories: ["R"]
tags: ["Top 100 Video Games", "Sales", "Region"]
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(collapse = TRUE)
```

# Region Sales Visuals

Below are Top 100 video games sold in millions in North America, Europe, Japan and other regions. Click directly on the chart or use the filter below to explore the content. You are also welcome to use the tabs in the upper right corner of the chart to decide whether to show the closest data on hover or to compare the sales differences of video games with the same ranking across all four regions on hover.

```{r message=F,warning=F,echo=F}
library(ggplot2)
library(plotly)
library(data.table)
data.file<-"../vgsales.csv"
fread(data.file)->info

salesCols<-c('Rank','Name',grep('_Sales$',names(info),value=T))
top100<-info[order(-Global_Sales)][1:100,..salesCols][,!'Global_Sales']
top100<-melt(top100,id.vars=c('Rank','Name'),variable.name='where',value.name='sales')
top100[,Region:=fcase(where=='NA_Sales','North America',where=='EU_Sales','Europe',where=='JP_Sales','Japan',default='Other')]

top100[,label:=
paste(paste0('<b>Rank</b>',': ',Rank),
paste0('<b>Name</b>',': ',Name),
paste0('<b>',Region,' Sales</b>',': ',sales),
sep="<br>")]

top100<-highlight_key(top100, ~Region, 'Select Region:')

pp<-ggplot(top100, aes(x = Rank,y = sales,colour = Region,group = Region,text = label))+
geom_line()+
  theme_bw() %+replace% theme(legend.position='bottom')+
  scale_x_continuous(expand = expansion(0.01),breaks = seq(10, 100, by = 10))+
  labs(y ='Sales')

ggplotly(pp, tooltip = 'label', width = 800) %>% 
  highlight(dynamic = F, selectize = T, opacityDim = 0.2) %>%
  layout(legend = list(orientation = "h",x = 0.5,xanchor = "center",y = -0.2),
         title=list(text='<b> North America, Europe, Japan and Other Sales of Top 100 Video Games (in millions) <b>', x = 0.5, xref = 'paper', font=list(size=15)))


```

